---
title: "Project 3"
resource_files:
- .Renviron
output:
  html_notebook:
    code_folding: hide
    toc: yes
    toc_depth: 4
    toc_float: yes
runtime: shiny
---


```{r setup, include=FALSE}
library(tidyverse)
library(data.world)
library(shiny)
knitr::opts_chunk$set(echo = TRUE)
```

## **Github Link** 
[Team 3 github](https://github.com/omar-olivarez/F17eDVProject3)

## **Introduction** 

The following analyses will observe trends in internet usage across the United State while also taking advantage of US Census Data.

## **Description of the dataset:** 
The Internet usage dataset contains...

```{r}
project <- "https://data.world/kassandra-perez/internet-usage"
data.world::set_config(cfg_env("DW_API"))
df <- data.world::query(data.world::qry_sql("SELECT * FROM internet-usage"), dataset = project)
```

## Scatter plot of internet usage at home against internet usage at work

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
