---
title: "Project 3"
resource_files:
- .Renviron
output:
  html_notebook:
    code_folding: hide
    toc: yes
    toc_depth: 4
    toc_float: yes
runtime: shiny
---


```{r setup, include=FALSE}
library(tidyverse)
library(data.world)
library(shiny)
knitr::opts_chunk$set(echo = TRUE)
```

## **Github Link** 
[Team 3 github](https://github.com/omar-olivarez/F17eDVProject3)

## **Introduction** 

The following analyses will observe trends in internet usage across the United State while also taking advantage of US Census Data.

## **Description of the dataset:** 
This data describes Internet Usage and Connectivity across the United States from July 2015 to October 2016. The columns that we used were a combination of the census population data,income data, internet usage and connectivity data.

[Original Dataset](http://www.governing.com/gov-data/internet-usage-by-state.html)

```{r}
project <- "https://data.world/kassandra-perez/internet-usage"
data.world::set_config(cfg_env("DW_API"))
df <- data.world::query(data.world::qry_sql("SELECT * FROM cleanedinternetusagebystate"), dataset = project)

states = df %>% dplyr::distinct(state)
```

## Internet Usage within different states

[Insight](https://data.world/kassandra-perez/f-17-edv-project-3/insights?anchor=https%3A%2F%2Fmedia.data.world%2Fy1DGViqGQDOAP3D6sAFm_image.png&id=7408d8f8-1973-45c5-b62a-06bc68370c1d&source=sb)

```{r}
renderPlot({
  ggplot(df) + geom_col(mapping = aes(x = state , y = internetusage)) + theme(axis.text.x = element_text(angle = 90, hjust = 1)) 
})

```

```{r}

inputPanel(
  selectInput("selectState", label = "State:",
              choices = states, multiple=FALSE, selected="Texas")
)

renderPlot({
  df %>% dplyr::filter(state == input$selectState) %>%ggplot() + geom_col(mapping = aes(x = state, y = internetusage,fill=internetusagelevel))
})

```

## Scatter plot of internet usage at home against internet usage at work

```{r}

renderPlot({
  ggplot(df) + geom_point(mapping = aes (x=internetusageathome,y=internetusageatwork))
})

```


## Boxplot 

[Insight](https://data.world/kassandra-perez/f-17-edv-project-3/insights/bdeb1f07-8337-42cc-985f-8724ac538efc)

```{r}
renderPlot({
  ggplot(df,mapping = aes(x = internetusageatworklevel,y = percapitaincome)) +
    geom_boxplot() 
})

```


## Facebook Users
```{r}
renderPlot({
  ggplot(df) + geom_col(mapping = aes(x = state,y = facebook_users_august_2010, fill = internetusagelevel)) + theme(axis.text.x = element_text(angle = 90, hjust = 1)) 
})

```

```{r}

inputPanel(
  selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50, 100), selected = 20)
)

renderPlot({
  ggplot(df, mapping = aes(x = facebook_penetration,fill = youngcategories)) + geom_histogram(bins=input$n_breaks)
})

```

```{r}
renderPlot({
  ggplot(df) + 
    geom_col(mapping = aes(x = youngcategories, y = facebook_users_august_2010, fill = youngcategories)) +
    facet_grid(.~internetusagelevel)
})

```
